Pillar 1 - Sequential Pattern Mining

### 2019-02-18 Pillar 1 - Sequential Pattern Mining.Rmd

  data %>%
    filter(
      !is.na(!!enquo(var))
      ) %>%
    group_by(
      !!enquo(var)
      ) %>%

    summarise(
      Count           = n(),
      Min             = min(Grade),
      Max             = max(Grade),
      Mean            = mean(Grade),
      Median          = median(Grade),
      IQR             = IQR(Grade),
      SD              = sd(Grade),
      `Low Rate`      = mean(Grade < high_grade),
      `Fail Rate`     = mean(Grade < pass_grade)
      ) %>%

    mutate_at(
      vars(Mean, SD, `Low Rate`, `Fail Rate`),
      round,
      digits = 2
    )

@@

```{r for convenience II}
course_all  <- unique(d_transactions$taken_PF_HL$item      )
student_all <- unique(d_transactions$taken_PF_HL$sequenceID)
n_students  <- length(student_all)
```

@@

  # Spread along ceiling grades
  mutate(
    grade_ceil = ceiling(Grade),
    Values     = TRUE
    ) %>%
  spread(
    key   = grade_ceil, 
    value = Values
    ) %>%

>>>>

    mutate(
      Grade = case_when(
        Grade >= 5.5 ~ Grade,
        T            ~ as.numeric(NA)
        )
      ) %>%

    filter(
      !is.na(!!enquo(var))
      ) %>%
    group_by(
      !!enquo(var)
      ) %>%

    summarise(
      Count           = n(),
      Min             = min(Grade, na.rm = TRUE),
      Max             = max(Grade, na.rm = TRUE),
      Mean            = mean(Grade, na.rm = TRUE),
      Median          = median(Grade, na.rm = TRUE),
      IQR             = IQR(Grade, na.rm = TRUE),
      SD              = sd(Grade, na.rm = TRUE),
      `Low Rate`      = mean(is.na(Grade) | Grade < high_grade),
      `Fail Rate`     = mean(is.na(Grade))
      ) %>%

    mutate_at(
      vars(Mean, SD, `Low Rate`, `Fail Rate`, IQR),
      round,
      digits = 2
    )

@@

For convenience:
```{r for convenience II}
course_all  <- unique(d_transactions$taken_PF_HL$item      )
student_all <- unique(d_transactions$taken_PF_HL$sequenceID)
n_students  <- length(student_all)
```

@@

  # Spread along ceiling grades
  mutate(
    grade_ceil = ceiling(Grade),
    Values     = TRUE,
    id         = 1 : n() # to ensure each row is unique
    ) %>%
  spread(
    key   = grade_ceil, 
    value = Values
    ) %>%
